### 2014-12-10 branches/kevin/docs/targetdp.tex
branch update passing tests
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2558 40876441-3496-0410-a613-a2fca35b2ae2

\end{lstlisting}
Here, an implementation with either uniform or separate address
spaces must arrange a copy of the data at appropriate times so
that any updates to \texttt{host} are correctly reflected
in \texttt{target}. All kernel-related references are again through
\texttt{target}.
The slightly disjoint nature of this definition and increased pressure
on global name-space must be weighed against potential increase in kernel
performance and reduction in register pressure.

@@

>>>>

\end{lstlisting}
Here, an implementation with either uniform or separate address
spaces must arrange a copy of the data at appropriate times so
that any updates to \texttt{host} are correctly reflected
in \texttt{target}. All kernel-related references are again through
\texttt{target}.
The slightly disjoint nature of this definition and increased pressure
on global name-space must be weighed against potential increase in kernel
performance and reduction in register pressure. More seriously, thre is
no way to write consistent \texttt{\_\_host\_\_ \_\_target\_\_} functions
(we can see) except to move the host structure back to file scope to
match the situation in the previous section.

@@

An attractive feature about this situation is that one can use the
uniform picture in memory to write functions of contract
\begin{lstlisting}
__host__ __target__ int obj_function(struct obj_kernel_data * obj, ...);
\end{lstlisting}
which can be used in both host and kernel code.
